\unnumberedChapter[issues]{Issues}
The goal of this chapter is to document the different issues that we faced during the creation of the following document and the development of the project in general.

\unnumberedSection[teamFormation]{Team Formation}
First of all, we had some problems to set the first official kick-off meeting because one of the member of the team was barely answering to the communications and did not even the invitations links to the \textit{Slack} channel neither the \textit{GitHub} repository. Before the handing of the first assignment, its name, \textbf{Carlos Cantos Morote}, has been removed from the documents and the team agreed to kick him out of the team.

\unnumberedSection[deadline]{First Delivery Deadline}
We must admit that it was quite challenging to produce as much information in the time we had to do it. In addition to the production of the report, the team had to find a concept for the game. We managed to find an idea relatively quickly, but a lot of implementation details are still missing to correctly and fully create the requested artifacts.

\unnumberedSection[graphics]{Graphics}
We have no graphical experience within the group, and as we look at other mobile games, it becomes apparent that a simple graphical look is something we wish to achieve during this project. This is to make the game more appealing to the users.

\unnumberedSection[p2p]{Peer-to-Peer Connection}
Since we rely on peer-to-peer to transfer the data between devices, we might encounter problems with devices that are unstable. How we will we handle bad devices potentially crashing game sessions and ruining the experience for other players.
