\unnumberedChapter[issues]{Issues}
The goal of this chapter is to document the different issues that we faced during the creation of the following document and the development of the project in general.

\unnumberedSection[firstExperienceECS]{First Experience with ECS Pattern}
Even thought half of the best members were really familiar with the \gls{ecs} pattern, it was a first time for the reset of the team. A lot of time has been spent on learning on the pattern works instead of developing features. This contributed too a huge reduction of effective time devoted to the project.

\unnumberedSection[poorPeerReview]{Poor Peer-Review Process}
Early stage of the project, we have been too loose on the approving of pull requests. Ask for refactoring, no generally accepted coding standards. Established new peer-review process within 24h and testing before accepting.

\unnumberedSection[tooManyDeliverable]{Too Many Deliverable}
Having so many deliverables made the whole project even more difficult to manage. Pushing some members to be fully in charge of specific deliverable without time for peer-reviewing

\unnumberedSection[highExpectations]{High Expectations}
The team members had unrealistic expectations about the final product given the time provided to do the project. We would not have complained if this project has to be delivered at the end of semester at the same time of the exam... Moreover, we were a bit too ambitious with what we wanted to create, which resulted in a lot of overtime spent developing the game. As this is only a 7.5 point course, we definitely spent too much time on it.\footnote{See \url{https://github.com/SamuelCabralCruz/tdt4240-project}}

\unnumberedSection[graphicDesign]{Graphic Designing}
As predicted in the architecture document, the fact that no member of the team had experience with graphic designing did not help to the situation. A lot of time has been invest just to create assets and textures.

\unnumberedSection[gpgsDowntime]{Google Play Services Downtime}
During our time developing the game, \textit{Google Play} services had some issues where the service itself was unavailable. This caused a pretty significant delay in our development, as we were unable to test the implementation of the service. This seems to still be an ongoing issue, according to the forums for the service, so we chose not to publish the game since it works in its current state.
