\unnumberedSection[scopeReduction]{Scope Reduction}

Many factors participated to the time limitation we experienced. The first and most foreseeable factor was the project scope which was, since the start of this project, too important for a team of 4 part-time developers. The fact that the developers are also students with a lot of other obligations did not help the case neither. It is also worth mentioning that 2 out of the 4 developers were also graduating bachelor students with a thesis to be delivered by the end of semester which has obviously took a lot of their time to the detriment of the project. As if, this was not enough, 3 members out of 4 have fallen sick during the semester leading to an overall lost of two weeks over the project schedule. As mentioned in the \nameref{chap:issues}, half of the team members did not have any prior experience with \gls{ecs} pattern. As powerful this pattern might be, as difficult it is to become familiar and efficient with it. Therefore, a lot of time has been invested in the learning of this pattern and how to properly implement it instead of developing new features having as effect to reduce even more the project time. Finally, the team put a lot of efforts to make the game looks as professional as possible. As flagged during the
\textit{Architecture Phase}, the fact that we did not have access to our own graphic designer required a lot of time just for the production of assets before even starting to do something out of them. Finally, as the same time as the game was being developed, the project management kept adding new features to the project's scope which lead to an inevitable \textit{Scope Creep}. \cite{scopeCreep} \\

With all these factors combined, it was clearly impossible to implement all the features in the product backlog. A prioritizing task has then been requested and here is a short list of postponed features:

\begin{multicols}{2}
  \begin{itemize}
    \item Results and Rematch Activity
    \item Game Mode Selection
    \item Single Player Mode
    \item Tutorial Mode
    \item Team Death Match Mode
    \item Capture the Flag Mode
    \item Character Selection
    \item Ultimate Powers
    \item \gls{npc} Characters
    \item Character Animations (Partly)
    \item Map Selection
    \item Random Map Generation
    \item Character Respawning
    \item Achievements
    \item Highscore User Classification
  \end{itemize}
\end{multicols}

On the other hand, the team still have been able to deliver the core of a really promising game with no apparent limitation regarding its architecture over what this game could become apart from some networking constraints from \gls{gpgs} that were out of our control. Thus, when we bring the project back into the context of the course, we can say that the main goal of this project has been achieved. Notwithstanding, it would be unfair to list all those feature without insisting on the fact that the only reason why they did not have been implemented is only because of time constraint because the current architecture would easily allow their realization.
