\unnumberedChapter[testReport]{Test Report}

This chapter will reuse all the requirements (functional and quality) formulated in the requirement document and asses if the final product have achieved them.

\FUNCTEST{F1: Pressing the settings buttons should change the view to the settings screen}
{Samuel}
{18.04.2018}
{30 seconds}
{success}
{Responsive feedback when pressing the menu buttons and the screen change immediately.}

\FUNCTEST{F2: Changing the audio settings should change the audio levels in game}
{Erling}
{12.04.2018}
{40 seconds}
{success}
{The audio levels from sound effects and music match the expected values when changing them in the menu.}

\FUNCTEST{F3: The credits screen should me scrollable}
{Samuel}
{27.03.2018}
{20 seconds}
{success}
{The scrolling is responsive and smooth. Able to go back to the main menu using the button at the bottom.}

\FUNCTEST{F4: When pressing “find room” the game should start the waiting room activity}
{Erling}
{01.04.2018}
{50 seconds}
{success}
{The activity successfully launches and show what participants are in the waiting room. At times the service could become unavailable, due to new issues at Google play service’s end.}

\FUNCTEST{F5: When using the joystick, the character should move accordingly}
{Jarle}
{03.04.2018}
{1 minute}
{success}
{The direction is correct, and the speed of the movement is also based on how far you move the joystick.}

\FUNCTEST{F6: when pressing the bomb button, there should spawn a bomb on the player location}
{Bart}
{07.04.2018}
{40 seconds}
{success}
{The bomb entity spawn successfully.}

\FUNCTEST{F7: when the timer component of a bomb runs out, it should spawn explosion entities around it}
{Erling}
{07.04.2018}
{40 seconds}
{success}
{Explosion entities successfully spawn and spread in expected directions.}

\FUNCTEST{F8: If an explosion entity hits a bomb entity, the bomb timer component should reach 0 and detonate}
{Erling}
{07.04.2018}
{40 seconds}
{success}
{Explosions are able to immediately detonate other bomb entities.}

\FUNCTEST{F9: If an explosion entity hits a crate entity, the crate should be destroyed}
{Samuel}
{16.04.2018}
{40 seconds}
{success}
{Crates are destroyed.}

\FUNCTEST{F10: If a player gets hit by an explosion entity, it should lose health}
{Bart}
{18.04.2018}
{40 seconds}
{success}
{Health bar is updated correctly.}

\FUNCTEST{F11: If a player picks up an upgrade, the HUD and actual behavior of the game should match expected value}
{Erling}
{20.04.2018}
{40 seconds}
{success}
{All the \gls{hud} elements update, and the behavior of the entities utilizing those values get their attributes updated correctly.}

\FUNCTEST{F12: If a remote player spawns a bomb, the local game for the local player should display that bomb}
{Jarle and Erling}
{19.04.2018}
{40 seconds}
{success}
{All bombs are placed in the correct place and synced properly.}

\FUNCTEST{F13: when you move around in your game, the other player should see your updated position and movement}
{Jarle and Erling}
{19.04.2018}
{40 seconds}
{success}
{Movement and position matches correctly between the clients, and additional linear interpolation makes the movement of the remote player smooooooooth.}

\FUNCTEST{F14 when leaving a google play room, you get redirected to the main menu}
{Bart}
{13.04.2018}
{40 seconds}
{success}
{View is changed correctly, and remote players are notified of this event.}
