\unnumberedChapter[ownExperienceAtam]{Own Experiences from Using \gls{atam}}
In this chapter we will describe how it was to use \gls{atam} to review and discuss the architect of the other group.

\unnumberedSection[uncovered]{What we uncovered}
During this process, we were able to uncover the fact that the other group's choice of wanting to implement state resynchronisation, and addressed how this will be very complicated and possibly affect the performance of their system. In uncovering this, we were able to let them know how this is a risk, and gave them the opportunity to reconsider their approach to this issue in their architecture.

\unnumberedSection[thoughts]{Thoughts about \gls{atam}}
As discussed in the previous chapter, using \gls{atam} we were able to let the other team know of the risks their architecture could contain in trying to achieve their attempts to support their quality attributes to meet the business goals.
Even though we were able to use the \gls{atam} process to achieve this, we didn't feel like the process itself was that relevant for this. When working on a relatively small project like this, we didn't feel like we benefited that much from it. We believe using \gls{atam} and benefit from it will be a lot more relevant when working on way larger projects, and have stakeholders that have technical competence in what field the software will be used participating in the process. 

Even though we were able to notify the other group of risks using this process, we believe this sort of risk would've been uncovered anyway if they had looked further into the offers they can get from \gls{gpgs}, as they already have solutions for syncing and detecting disconnected players.

We agree with the benefits of discovering flaws in the architect before starting the coding, as this will save a lot of time and frustration, but we believe if we were to develop a bigger system, and cooperate with other participants than just being on our own developing a game from scratch, we might have been able to benefit more from \gls{atam}.